---
title: "Lab 5"
author: "Yutian Fang"
date: "10/25/2021"
output: 
  html_document: 
    theme: united
    toc: yes
    code_folding: hide
---

```{r setup, include=TRUE, message = FALSE, warning= FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)
library(tidyverse)
library(effsize)
```

## Part 1: Confidence Intervals

In this section, we'll use the 't.test()' function to calculate confidence intervals.

### Example 1
Create a single mock sample containing a number of values, then learn to use 't.test()' to return confidence intervals, and learn about in-line code referencing so our text becomes more reproducible too.
```{r}
#Create a mock sample
otter_length <- c(30,45,28,31,34,46,52,29)

#Find the confidence interval:
otter_ci <- t.test(otter_length)

#95% CI: If we take multiple samples from the population and calculate sample mean, we will expect 95% of the chance the true population mean (parameters) will fall into this interval

#Find the standard deviation
otter_sd <- sd(otter_length)
```
Mean otter length is 36.9 inches $\pm$ 9.3 (mean $\pm$ sd, n = 8) with a 95% confidence interval of [29.1,44.7] inches

#### Now, using in-line referencing

Mean otter length is `r round(otter_ci$estimate, 1)` inches


