---
title: "Lab 5"
author: "Yutian Fang"
date: "10/25/2021"
output: 
  html_document: 
    theme: united
    toc: yes
    code_folding: hide
---

```{r setup, include=TRUE, message = FALSE, warning= FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)
library(tidyverse)
library(effsize)
```

## Part 1: Confidence Intervals

In this section, we'll use the 't.test()' function to calculate confidence intervals.

### Example 1
Create a single mock sample containing a number of values, then learn to use 't.test()' to return confidence intervals, and learn about in-line code referencing so our text becomes more reproducible too.
```{r}
#Create a mock sample
otter_length <- c(30,45,28,31,34,46,52,29)

#Find the confidence interval:
otter_ci <- t.test(otter_length)

#95% CI: If we take multiple samples from the population and calculate sample mean, we will expect 95% of the chance the true population mean (parameters) will fall into this interval

#Find the standard deviation
otter_sd <- sd(otter_length)
```
Mean otter length is 36.9 inches $\pm$ 9.3 (mean $\pm$ sd, n = 8) with a 95% confidence interval of [29.1,44.7] inches

#### Now, using in-line referencing

Mean otter length is `r round(otter_ci$estimate, 1)` inches with a 95% confidence interval of [`r round(otter_ci$conf.int[1],1)`,`r round(otter_ci$conf.int[2],1)`] inches.

## Part 2: Two-sample t-tests

### Example 1 

Make two mock samples, and ask the question: do we have sufficient evidence to make us reject the null hypothesis that these samples were drawn from populations with the same mean?
```{r}
# Make my mock samples
oak_trees <- c(20,19,24,28,34,12,15,25)
  
pine_trees <- c(39,26,20,30,37,22,19,18)

# Two-sample t-test
tree_t <- t.test(oak_trees, pine_trees)

# Null hypothesis: mean heights are the same
# ie.: Trees are drawn from populations with the same mean height
# p-value: If these samples were drawn from the samples with the same mean height, then there is a 28% chance of taking random samples and find sample means are at least this difference (from -1.1 to 1.1) by random chance
```

The mean heights of oak and pine trees were (X +- Y) and (X +- Y), respectively, and the difference was not significant (t(`r round(tree_t$parameter,1)`) = `r round(tree_t$statistic,1)`, p =`r round(tree_t$p.value,1)`). 

"t(df) = t-statistic, p = p-value"

*AVOID*: P = 0
When things get really small (usually p <0.001)

*Not great:* p= 0.00000013
*Better*:* p <0.001

## Part 3: Another t-test with cars data

Using the 'mpg' dataset

### Take a look at the data
```{r}
compact_suv <- mpg %>%
  filter(class %in% c("compact","suv"))

# Check for remaining levels
unique(compact_suv$class)
```

Create a histogram of city gas mileage (cty) faceted by class starting from compact_suv
```{r}
library(ggplot2)
ggplot(data = compact_suv, aes(x= cty)) + 
  geom_histogram(bins = 10)+
  facet_wrap(~class)

ggplot(data = compact_suv, aes(sample = cty)) +
  geom_qq() +
  facet_wrap(~class)
```

Find some summary statistics for each group.

```{r}
car_stats <- compact_suv%>%
  group_by(class)%>%
  summarize(
    mean_city = mean(cty),
    sd_city = sd(cty),
    sample_size = n()
  )

car_stats
```

The t.test() function REALLY wants vectors of things, Use the `pull()` function to pull out a vector from a data frame

```{r}
compact_sample <- compact_suv %>%
  filter(class == "compact")%>%
  pull(cty)

suv_sample <- compact_suv %>%
  filter(class == "suv") %>%
  pull(cty)

```

H0: Mean city gas mileages for SUVs and compact cars are the same
```{r}
t.test(compact_sample, suv_sample)
```

There is a significant difference in mean city gas mileage for SUVs and compact cars (t(df) = t-statistic, p<0.001)
